---
title: 'NFL Stats: 2005-2015'
author: ''
date: "December 19, 2015"
output: html_document
---

###Summary + Description of Data
This is an attempt to learn R Markdown and incorporate historical and current NFL data from 2005-2015 from [NFL.com](http://www.nfl.com/stats/team). This analysis will (hopefully) consist of plots and tables and hopefully some interesting trends I discover as I work through this stuff. I'm really just interested in seeing if I can get this to update as the 2015 regular season progresses.


The data consists of `r ncol(stats)` offensive and defensive variables by season for each of the 32 teams in the NFL, which comes to `r nrow(stats)` observations of each variable. In 2015, the `r team.pts.2015[1,1]` have the highest average points per game at `r team.pts.2015[1,2]` points, follwoed by the `r team.pts.2015[2,1]` and `r team.pts.2015[3,1]` scoring on average `r team.pts.2015[2,2]` and `r team.pts.2015[3,2]` points, respectively. A table of the top ten teams organized by average points over the past 10 seasons is below:

```{r, echo = FALSE, results = "asis", align = "c"}
knitr::kable(head(team.pts, n=10), digits=2, format="html", table.attr = "width=\"400\"")

```

--------

The plot below indicates the amount of penatly yards seems to have no real effect on the amount of points per game scored. The pearson correlation for these two variables is `r round(cor(stats$pen.yds, stats$pts.game), digits = 4)`, which confirms the lack of relationship shown in the plot.

```{r, echo = FALSE}
print(pts.vs.pen)
```


