---
title: 'NFL Stats: 2005-2015'
author: ''
date: "December 19, 2015"
output: html_document
---

###Summary + Description of Data
This is an attempt to learn R Markdown and incorporate historical and current NFL data from 2005-2015 from [NFL.com](http://www.nfl.com/stats/team). This analysis will (hopefully) consist of plots and tables and any interesting trends I discover as I work through this stuff. I'm really just interested in seeing if I can get this to update as the 2015 regular season progresses.


The data consists of `r ncol(stats)` offensive and defensive variables by season for each of the 32 teams in the NFL, which comes to `r nrow(stats)` observations of each variable. In 2015, the `r team.pts.2015[1,1]` have the highest average points per game at `r team.pts.2015[1,2]` points, followed by the `r team.pts.2015[2,1]` and `r team.pts.2015[3,1]` scoring on average `r team.pts.2015[2,2]` and `r team.pts.2015[3,2]` points, respectively. Looking back over the past 10 seasons, the `r team.pts[1,1]` on average scored the most points per game.

```{r, echo = FALSE, results = "asis", align = "c"}
knitr::kable(head(team.pts, n=10), digits=2)

```


The plot below indicates the amount of penalty yards seems to have no real effect on the amount of points per game scored. The Pearson correlation for these two variables is basically 0 (r=`r round(cor((stats$pen.yds/stats$games), stats$pts.game), digits = 4)`), which confirms the lack of relationship shown in the plot. Thought this was lind of interesting, maybe coahces/fans should't be too upset at enalties that cost a lot of yards.

```{r, echo = FALSE, fig.width=8, fig.height=7}

print(pts.vs.pen.yds)

```

A plot of ponts per game against the number of pentalties per game shows a similar (non) relationship.

```{r, echo = FALSE, fig.width=8, fig.height=7}

print(pts.vs.pen)

```

